Title of submission to PLOS journal

### 2023-03-22 paper/help/old/paper.Rmd

---
title: Digital economy in the UK: a multi-scalar story of the diffusion of web technologies
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    correspondingauthor: true
    footnote: 1
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.

keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---
# Introduction {#sec:1}

@@

<!-- motivation -->

>>>>

---
title: Title of submission to PLOS journal
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    corresponding: e.tranos@bristol.ac.uk
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
abstract: |
  blah blah

author_summary: |
  blah blah
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo=FALSE, message = FALSE, warning=FALSE}
library(stargazer)
library(tidyverse)
#library(rmarkdown)
```

# Introduction {#sec:1}

@@

<!-- motivation -->
@meade2021modelling There are numerous agents who would benefit from
accurate predictions of introduction times. These include: suppliers of
network equipment for production planning; suppliers of mobile phones
who need to have inventories of appropriately configured handsets;
international network planners who need to provide sufficient bandwidth
for communications between different countries; network operators and
regulatory authorities.
